HW! - Regression Model - 621

### 2020-09-10 HW1/reg_model_shamp.Rmd
fix data load files

```{r}
set.seed(9450)
train_df<- 
  read.csv("/Users/jeffshamp/Documents/Github/DT621_Fall2020_Group2/HW1/data/moneyball-training-data.csv")
train_df<- 
  train_df %>% 
  select(-c(TEAM_BATTING_HBP, INDEX)) %>%
  mutate_if(is.integer, as.numeric)
```

@@

```{r}
cooks_dis<- cooks.distance(lm_1)
influential<- as.numeric(names(cooks_dis)[(cooks_dis > (4/nrow(train_df)))])
train_df<- train_df[-influential, ]
```

@@

```{r}
test_df<- 
  read.csv("/Users/jeffshamp/Documents/Github/DT621_Fall2020_Group2/HW1/data/moneyball-evaluation-data.csv")
test_df<- 
  test_df %>% 
  select(-c(TEAM_BATTING_HBP, INDEX)) %>%
  mutate(TEAM_BATTING_1B =
         TEAM_BATTING_H -
         (TEAM_BATTING_2B + TEAM_BATTING_3B + TEAM_BATTING_HR)) %>%
  mutate_if(is.integer, as.numeric)

>>>>

```{r}
set.seed(9450)
train_df<- 
  read.csv("./data/moneyball-training-data.csv")
train_df <-
  train_df %>%
  select(-c(TEAM_BATTING_HBP, -INDEX)) %>%
  mutate_if(is.integer, as.numeric)
```

@@

```{r}
# Base R, disgusting
cooks_dis<- cooks.distance(lm_1)
influential<- as.numeric(names(cooks_dis)[(cooks_dis > (4/nrow(train_df)))])
train_df<- train_df[-influential, ]
```

@@

```{r}
test_df<- 
  read.csv("./data/moneyball-evaluation-data.csv")
test_df<- 
  test_df %>% 
  select(-c(TEAM_BATTING_HBP, INDEX)) %>%
  mutate(TEAM_BATTING_1B =
         TEAM_BATTING_H -
         (TEAM_BATTING_2B + TEAM_BATTING_3B + TEAM_BATTING_HR)) %>%
  mutate_if(is.integer, as.numeric)
